Fractional Types

### 2016-12-16 typespp.tex
small changes

If we are to build a compositional programming language around iteration and
symmetry groupoids, we need to ensure that they compose sensibly with the
existing type formers. Groupoids, viewed as categories, come associated with
natural notions of sums and products, and one might expect or hope that
identities which hold for rational numbers lift to identities in our
situation. The most prominent and important identity we seek is:
such as:
\[
\order{p} \otimes \iorder{p} \simeq \mathbb{1}
\]
The groupoids on either side are not categorically equivalent but they do have the same cardinality. Thus if we focus on some notion of cardinality-preserving morphisms, it is sensible to consider them equivalent. The situation is however subtle and does not directly support a notion of sums. It is studied in detail in the next section.

@@

>>>>

@@

If we are to build a compositional programming language around iteration and
symmetry groupoids, we need to ensure that they compose sensibly with the
existing type formers. Groupoids, viewed as categories, come associated with
natural notions of sums and products, and one might expect or hope that
identities which hold for rational numbers lift to identities in our
situation. The most prominent and important identity we seek is:
\[
\order{p} \otimes \iorder{p} \simeq \mathbb{1}
\]
for some appropriate unit object $\mathbb{1}$. The groupoids on either side are not categorically equivalent but they do have the same cardinality. Furthermore the iteration groupoid and the symmetry groupoid naturally ``cancel out'' in the sense that the iteration groupoid introduces the iterates of a combinator $c$ as separate objects while the symmetry groupoid uses these same iterates to express internal symmetries. Thus if we focus on the right notion of morphisms, it is sensible to consider them equivalent. The situation is however subtle and does not directly support a notion of sums. It is studied in detail in the next section.
